Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-10-03 paper/changes.tex
Replaced Relative MSE values by RMSE, including reviewer's comment on DART in changes.pdf

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
 Algebraic Reconstruction Technique (SART)~\cite{sart}. We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
 is no prior information about the number of possible attentuation
 coefficients in the test object.
%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
 Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

\begin{table}[!h]
  \centering
 \caption{RMSE of reconstructions from various
    methods within the RoI.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
&\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline \textbf{Potato}& 0.29 & 0.24 & \textcolor{red}{0.18}
\\ \hline \textbf{Sprouts}& 0.53 & 0.48 & \textcolor{red}{0.30}
\\ \hline \textbf{Liver}& 0.05 & 0.17 & \textcolor{red}{0.03}
\\ \hline
\end{tabular}
\label{table:rmse}
\end{table}

>>>>

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
 Algebraic Reconstruction Technique (SART)~\cite{sart}. 
%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
 Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

 \item \textcolor{blue}{The paper would be improved by including results from more methods, for example ...DART}\\
   We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
 is no prior information about the number of possible attentuation
 coefficients in the test object.

@@

\begin{table}[!h]
  \centering
 \caption{RMSE of reconstructions from various
    methods within the RoI.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
&\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline \textbf{Potato}& (from paper)  &  & \textcolor{red}{}
\\ \hline \textbf{Sprouts}&  &  & \textcolor{red}{}
\\ \hline \textbf{Liver}&  &  & \textcolor{red}{}
\\ \hline
\end{tabular}
\label{table:rmse}
\end{table}

### 2021-10-03 paper/post_tci.tex
Replaced Relative MSE values by RMSE, including reviewer's comment on DART in changes.pdf

\caption{SSIM and Relative MSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ideal reconstruction is 1.}

@@

Rel.MSE & 0.33 & 0.07 & 0.14 & 0.41 & 0.24 & 0.1 & 0.03 & \textcolor{red}{0.00}\\ \hline

@@

We observe
that our method reconstructs new structures while simultaneously
reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM of
the reconstructed new regions using various methods.
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
\label{fig:potato_zoomed_2D_results}
\end{figure}
\end{comment}
%-------------------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (Relative MSE) of reconstructed potato from various
    methods. The SSIM of ideal reconstruction is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.52 / 0.16
& 0.92 / 0.00 & \textcolor{red}{0.97 / 0.00} \\ \hline \textbf{3D} & 0.58 / 0.29 & 0.75 / 0.24 & \textcolor{red}{0.84 / 0.18}
\\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (Relative MSE) of reconstructed okra from various
    methods. SSIM of the ideal reconstruction is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.46 / 0.22
& 0.50 / 0.16 & \textcolor{red}{0.74 / 0.06} \\ \hline \textbf{3D} & 0.65 / 0.35 & 0.70 / 0.32 & \textcolor{red}{0.71 / 0.29}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{The SSIM (Relative MSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ideal reconstruction, SSIM equals 1.}
\begin{tabular}{|l|c|c|c|c|}
\hline \textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline  0.73 / 0.05
& 0.91 / 0.17 & \textcolor{red}{0.95 / 0.03} \\ \hline 
\end{tabular}
\label{table:tmh_ssim}
\end{table}
%-----------------------------------------------------------------

@@

%----------------------------------------------------
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_zoomed.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
\label{fig:sprouts_zoomed_2D_results}
\end{figure}
\end{comment}
%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (Relative MSE) of reconstructed sprouts from various
    methods. The SSIM of ideal reconstruction) is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
 \\ \hline \textbf{2D} & 0.67 / 0.23
& 0.82 / 0.12 & \textcolor{red}{0.86 / 0.07} \\ \hline \textbf{3D} & 0.67 / 0.53 & 0.73 / 0.48 & \textcolor{red}{0.82 / 0.30}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}

@@

\begin{table}[]
 \centering
  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver (refer code in~\cite{codeRepo}) on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM. Here we assume that low quality eigen-spaces of the templates are computed offline.}
\begin{tabular}{|l|l|l|l|}
\hline
 \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{6.00} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\subsection{Requirements for applying deep learning techniques}
Deep learning techniques are powerful tools to learn an unknown
parameteric function relating an input space and an output space. In such
settings, our current goal of detecting new changes is a `prediction'
problem in a continuous solution space i.e., \textit{``given
  intensities of a voxel at various time instants in a longitudinal
  setting and partial measurements of the voxel at the current time,
  what will be the intensity of the same voxel at the current time
  instant?''}. This estimation can be learnt by a deep neural network
if there are hundreds of labeled data.  However, generalization of
this across multiple datasets poses a question mark.

>>>>

\caption{SSIM and RMSE of the reconstructions shown in Fig.~\ref{fig:reconstructions_diff_methods}:(a)-(g). The SSIM of ideal reconstruction is 1.}

@@

RMSE & 0.38 & 0.18 & 0.25 & 0.43 & 0.33 & 0.21 & 0.11 & \textcolor{red}{0.04}\\ \hline

@@

We observe
that our method reconstructs new structures while simultaneously
reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM of
the reconstructed new regions using various methods.
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
\label{fig:potato_zoomed_2D_results}
\end{figure}
\end{comment}
%-------------------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (RMSE) of reconstructed potato from various
    methods. The SSIM of ideal reconstruction is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.52 (0.36)
& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
\\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (RMSE) of reconstructed okra from various
    methods. SSIM of the ideal reconstruction is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ \hline \textbf{3D, 30 views} & 0.69 (0.21) & 0.74 (0.30) & \textcolor{red}{0.78 (0.26)}\\
\hline \textbf{3D, 45 views} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{The SSIM (RMSE) of 2D reconstruction of radio-frequency ablation data from various methods. Values have been computed within the RoI. For ideal reconstruction, SSIM equals 1.}
\begin{tabular}{|l|c|c|c|c|}
\hline \textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline  0.73 (0.04)
& 0.91 (0.09) & \textcolor{red}{0.95 (0.03)} \\ \hline 
\end{tabular}
\label{table:tmh_ssim}
\end{table}
%-----------------------------------------------------------------

@@

%----------------------------------------------------
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_zoomed.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
\label{fig:sprouts_zoomed_2D_results}
\end{figure}
\end{comment}
%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{The SSIM (RMSE) of reconstructed sprouts from various
    methods. The SSIM of ideal reconstruction) is 1.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
 \\ \hline \textbf{2D} & 0.67 (0.24)
& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}

@@

\begin{table}[!h]
 \centering
  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver (refer code in~\cite{codeRepo}) on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM. Here we assume that low quality eigen-spaces of the templates are computed offline.}
\begin{tabular}{|l|l|l|l|}
\hline
 \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{5.63} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\subsection{Requirements for applying deep learning techniques}
Deep learning techniques are powerful tools to learn an unknown
parameteric function relating an input space and an output space. In such
settings, our current goal of detecting new changes is a `prediction'
problem in a continuous solution space i.e., \textit{``given
  intensities of a voxel at various time instants in a longitudinal
  setting and partial measurements of the voxel at the current time,
  what will be the intensity of the same voxel at the current time
  instant?''}. This estimation can be learnt by a deep neural network
if there are hundreds of labeled data.  However, generalization of
this across multiple datasets poses a question mark.
